---
title: "Big Book of Data Analysis"
author: "Fabrizio Veneziano"
date: "Wednesday, May 06, 2015"
output: html_document
---

```{r cache=T, echo=FALSE}
source('../LeadsLoader.R')
```

```{r echo=F}
source('GA_Loader.R')
```


# Where do our students come from?   
  
  
### NOTE: 'Student' = REG



```{r echo=F,}
#dat <- all.leads[as.Date(all.leads$CreatedDate)>"2014-03-01",]
dat <- all.leads
dat$online <- ifelse(dat$LeadSource %in% c("Paris Website","Madrid Website","Heidelberg Website","Schiller.edu Website"),"Online","Offline")

# All leads
# aggregate(Id~online,data=dat, length)
online.all <- table(dat$online)
online.all.prop <- round(prop.table(table(dat$online)),2)
# online.all.plot <- barplot(table(dat$online))

# REG only
# aggregate(Id~online,data=dat[dat$Status=="REG",], length)
online.REG <- table(dat$online[dat$Status=="REG"])
online.REG.prop <- round(prop.table(table(dat$online[dat$Status=="REG"])),2)

```

According to our Salesforce database, out of `r sum(online.REG)` SIU Students (European Campuses only), `r online.REG.prop[2]*100`% come from an **online source**.

```{r echo=F}
online.REG.plot <- barplot(table(dat$online[dat$Status=="REG"]),col=c("darkblue","darkred"), main="Students (REG) by Source Type")
grid()
text(0.75,280,paste(online.REG.prop[1]*100,"%"), col="white")
text(1.85,280,paste(online.REG.prop[2]*100,"%"), col="black")

```

In theory, the `r online.REG[2]` students who reach us via our websites, could be broken down in **channels**, that is possible ways users have of landing on a website. These are industry standard categories (Google flavors, at least), and range from visits from search engine to visits initiated by a mass emailing from our Admission Dept. However, both for technical and legal reasons^[Google Analytics sometimes simply is unable to register such information. Moreover, privacy considerations may discorage us from tracking users too closely.], it's not always easy to inject such information from Google Analytics into Salesforce, and in fact the information available to us in this sense is partial and only `r sum(table(dat$Campaign_Medium__c[dat$Status=="REG"]))` students (REG) out of `r sum(online.REG)` can be assigned to a web channel.  
  
On the other hand, What we can do, is widen our viewpoint and extend it to (web)lead rather than stricly students (REG). In this latter case

```{r}

PA.channels <- aggregate(sessions~medium,data=GA.paris,sum)
PA.channels <- subset(PA.channels, PA.channels$sessions > 10)

```




  *  Global
    *  Paris
    *  Madrid
    *  Heidelberg

# Typical profile(s) of REG
- demographic
- behavior on site (time, pageviews, etc)

# Notable profile(s) of almost REG and of almost leads
Are there sizeable groups of users who:
- Send info request but do not become REG or Qualified?
- Land on the website(s) but do not fill the form?


```{r}

```


